Spfy: an integrated graph database for real-time prediction of Escherichia coli phenotypes and downstream comparative analyses

### 2018-04-19 paper-webserver.tex
CHANGE: made suggestions rec by Matt

% This is still true. The text needs to be larger: --> The text in this figure is too small to read and seems blurry. It should be enlarged.
\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/ontology}
\end{center}
\caption{Structure of the Spfy graph database. Brackets highlight the source of different data points and the software it was generated from. Data are added in as the analysis modules complete, at varying times, and the overall connections are inferred by the database. Non-bracketed sections are sourced from the uploaded genome files or user-supplied metadata.}
\label{fig-ontology}
\end{figure}

@@

\subsection{Continuous integration}
% Keep this short
% para
% 1. goals: why CI, testing is important
% 2. how we've implemented it, integration with github

% MW: I would remove this section. Its not that critical to anyone that uses Spfy and would be an individual
% choice for developers that obtain the code

Tests for functionality and backwards compatibility are run on TravisCI \url{https://travisci.io}, a continuous integration (CI) platform.
The individual tests use PyTest \url{https://doc.pytest.org/}, and the current build status can be checked on GitHub at \url{https://travis-ci.org/superphy/backend}.
TravisCI also builds the core Docker images for Spfy, and uploads them to Docker Hub \url{https://hub.docker.com/u/superphy/}.

@@

On analysis tasks, Spfy runs all included analyses modules in an average of 130 seconds per genome, as shown in Figure \ref{fig:spfy_performance_indivs}.
Spfy can also queue batches of genomes for analysis, decreasing the average runtime to an average of 54 seconds per file due to parallelization of analysis runs \ref{fig:spfy_performance_batches}.
In total, the platform analyzed 50 genomes in 45 minutes, and 100 genomes in 89 minutes.

% MW I would move the next 2 figures to supplementary information to cut down on figures
% Often there is a limit on the # of figs.

\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/spfy_indivs.png}
\end{center}
\caption{Runtimes of Spfy's analysis modules. 100 genomes were run individually, with each coloured dot representing the runtime of a separate analysis module. The blue line indicates the average actual runtime per file after accounting for parallelization.}\label{fig:spfy_performance_indivs}
\end{figure}

% Again, label panes as a) and b), then reference in the caption
\begin{figure}[!htb]
\minipage{0.5\textwidth}
  \includegraphics[width=\linewidth]{images/spfy_batches_totals.png}
\endminipage\hfill
\minipage{0.5\textwidth}%
  \includegraphics[width=\linewidth]{images/spfy_batches.png}
\endminipage
\caption{Runtimes of Spfy's analysis modules for batches of files. Left: Total runtime for analyzing all files in the given batch. The blue line indicates the actual time to completion after accounting for parallelization; 50 files are analyzed in 45 minutes and 100 files in 89 minutes. Right: Average runtime per file in the batch. As indicated by the line, the average runtime per genome in consistent when running more than one file due to the parallelization of analyses.}\label{fig:spfy_performance_batches}
\end{figure}

@@

>>>>

% This is still true. The text needs to be larger: --> The text in this figure is too small to read and seems blurry. It should be enlarged.
\begin{figure}[!hb]
\begin{center}
\includegraphics[width=\textwidth]{images/ontology_r3}
\end{center}
\caption{Structure of the Spfy graph database. Brackets highlight the source of different data points and the software it was generated from. Data are added in as the analysis modules complete, at varying times, and the overall connections are inferred by the database. Non-bracketed sections are sourced from the uploaded genome files or user-supplied metadata.}
\label{fig-ontology}
\end{figure}

@@

@@

On analysis tasks, Spfy runs all included analyses modules in an average of 130 seconds per genome.
Spfy can also queue batches of genomes for analysis, decreasing the average runtime to an average of 54 seconds per file due to parallelization of analysis runs \ref{fig:spfy_performance}.
In total, the platform analyzed 50 genomes in 45 minutes, and 100 genomes in 89 minutes.

\begin{figure}[!htb]
\minipage{0.5\textwidth}%
  \includegraphics[width=\linewidth]{images/spfy_batches_totals.png}
\endminipage
\caption{Total runtimes of Spfy's analysis modules for batches of files. The blue line indicates the actual time to completion after accounting for parallelization; 50 files are analyzed in 45 minutes and 100 files in 89 minutes.}\label{fig:spfy_performance}
\end{figure}

@@

\section{SUPPLEMENTARY INFORMATION}

% Again, label panes as a) and b), then reference in the caption
\begin{figure}[!htb]
\minipage{0.5\textwidth}
  \includegraphics[width=\linewidth]{images/spfy_indivs.png}
\endminipage\hfill
\minipage{0.5\textwidth}%
  \includegraphics[width=\linewidth]{images/spfy_batches.png}
\endminipage
\caption{Runtimes of Spfy's analysis modules. A: 100 genomes were run individually, with each coloured dot representing the runtime of a separate analysis module. The blue line indicates the average actual runtime per file after accounting for parallelization. B: Average runtime when multiple genomes are enqueued together. As indicated by the line, the average runtime per genome in consistent when running more than one file.}\label{fig:supp_spfy_performance}
\end{figure}
